Kyoto VR MQP Paper First Draft

### 2019-08-29 paper.tex
add more use cases

% add table of contents to itself
\addcontentsline{toc}{section}{Table of Contents}
\tableofcontents
\newpage

\addcontentsline{toc}{section}{List of Figures}
\listoffigures
\newpage

@@

\subsubsection{Current Augmented Reality Technology}
\label{sec:currentAugmentedRealityTechnology}

@@

@@

ARKit and ARCore are both AR frameworks that enable apps to take advantage of
powerful AR related features. ARKit is developed by Apple and can only be used
by iPhones. Google's ARCore framework can deploy to both Android and iPhone.
Many cross platform solutions will leverage the full potential of their target
platform by using either ARKit or ARCore "under the hood". Both ViroReact and
Vuforia use ARKit or ARCore depending on the target platform
\autocites{vuforiaFusion}{moon2018}.

ARKit 3 aims to support a wide array of new features, and will be available in
iOS 13. Notably, one of these features is "people occlusion," which will allow
virtual objects to be realistically obscured when someone walks in front of the
object~\autocite{apple2019}. This kind of technology could be useful for us
since our app uses AR in crowded places.  As of August, 2019, this feature is
not on the horizon for Google's Android AR framework, ARCore.

@@

The goal of Editour is to allow a non-technical user to design audio tours
through a web-app. At its core, Editour is a tool to draw arbitarily-shaped
geographic regions onto a map. An audio file and multiple image files can be
uploaded for each region the user defines. After naming and uploading the tour
with the "Upload" button, our backend builds a zip containing a folder that can
be placed directly into the Unity project.

@@

We chose Node.js as the server-side framework because of our prior experience
with JavaScript, its high-performing asynchronous architecture, and its ease of
development.

>>>>

% add table of contents to itself
\tableofcontents
\addcontentsline{toc}{section}{Table of Contents}
\newpage

\listoffigures
\addcontentsline{toc}{section}{List of Figures}
\newpage

@@

\subsection{Current Augmented Reality Technology}
\label{sec:currentAugmentedRealityTechnology}

@@

The video game industry has readily embraced augmented reality, leading to the
development of many AR games for smartphones and dedicated head-mounted
displays. Perhaps the most popular AR game, \textit{Pokémon Go}, has been
downloaded over a billion times~\autocite{webster2018}. This game makes use of
GPS and camera data to overlay game objects (in this case fictional monsters) on
top of images of the real world (see Figure
\ref{fig:pokemonGo})~\autocite{concepcion2016}.

\begin{figure}[h]
	\centering
	\includegraphics[width=.5\textwidth]{pokemon-go.jpg}
	\caption{A screenshot from the AR game \textit{Pokémon
			Go}~\autocite{vastateparks2016}.}
	\label{fig:pokemonGo}
\end{figure}

@@

ARKit and ARCore are both AR frameworks that enable apps to take advantage of
powerful AR related features. ARKit is developed by Apple and can only be used
by iPhones. Google's ARCore framework can deploy to both Android and iPhone.
Many cross platform solutions will leverage the full potential of their target
platform by using either ARKit or ARCore ``under the hood''. Both ViroReact and
Vuforia use ARKit or ARCore depending on the target platform
\autocites{vuforiaFusion}{moon2018}.

ARKit 3 aims to support a wide array of new features, and will be available in
iOS 13. Notably, one of these features is ``people occlusion,'' which will allow
virtual objects to be realistically obscured when someone walks in front of the
object~\autocite{apple2019}. This kind of technology could be useful for us
since our app uses AR in crowded places.  As of August, 2019, this feature is
not on the horizon for Google's Android AR framework, ARCore.

@@

The goal of Editour is to allow a non-technical user to design audio tours
through a web-app. At its core, Editour is a tool to draw arbitarily-shaped
geographic regions onto a map. An audio file and multiple image files can be
uploaded for each region the user defines. After naming and uploading the tour
with the ``Upload'' button, our backend builds a zip containing a folder that can
be placed directly into the Unity project.

@@

We chose Node.js as the server-side framework because of our prior experience
with JavaScript, its high-performing asynchronous
architecture~\autocite{orsini2013}, and its ease of development.
